Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2021-01-04 awipev-CO2.Rmd
clean up variable names

---
title: "Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project" 
author: "Jean-Pierre Gattuso and Samir Alliouane"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    theme: paper
    number_sections: false

@@

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
if (!require("tidyverse")) install.packages("tidyverse")
library(dplyr)
library(tidyverse)
if (!require("robfilter")) install.packages("robfilter")
if (!require("robfilter")) install.packages("robfilter")
library("robfilter")
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("reshape2")) install.packages("reshape2")
library("reshape2")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("lmtest")) install.packages("lmtest")
library("lmtest")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("seismicRoll")) install.packages("seismicRoll")
library("seismicRoll")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("cowplot")) install.packages("cowplot")
library(cowplot)
if (!require("htmlwidgets")) install.packages("htmlwidgets")
library("htmlwidgets")
if (!require("hms")) install.packages("hms")
library("hms")
if (!require("ragg")) install.packages("ragg")
library("ragg")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")

@@

```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2_corr = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  arrange(datetime)
d_all <- as_tibble(d_hour) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & pressure_insitu_ctd <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & pressure_insitu_ctd <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & pressure_insitu_ctd <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 9, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
  )
```

@@

# create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_fb <- NA
discrete_is_na$pco2_calc_fb <- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)
```
```{r read and prepare nutrient data, echo=FALSE, warning=TRUE, message=FALSE}
# File "Ferrybox nutrients 2014-2018.xlsx" provided by 
# Willem van de Poll <w.h.van.de.poll@rug.nl> on 2020-01-16
# nutrients in umol/l
nuts <- readxl::read_excel(paste0(path, "fb_data/Ferrybox nutrients 2014-2018.xlsx"),
                           skip =1) %>% 
  drop_na(date) %>% 
  dplyr::mutate(datetime = as.POSIXct(paste0(date, " 12:00:00"))) %>% # assuming sampling time 12:00
  dplyr::filter(datetime > as.POSIXct("2015-07-09"))
# The nearest times
time_index <- unique(d_all$datetime)
# nuts$closest <- time_index[
#   FNN::knnx.index(time_index, # The values to be queried (big df)
#                   as.vector(nuts$datetime), # The value to find the closest match to (small df)
#                   k = 1)] # The number of closest values to return
nuts <- nuts %>% 
  dplyr::mutate(closest = time_index[
  FNN::knnx.index(time_index, # The values to be queried (big df)
                  as.vector(nuts$datetime), # The value to find the closest match to (small df)
                  k = 1)]) %>%  # The number of closest values to return
  dplyr::select(-date, -datetime) %>% 
  dplyr::rename(NO3NO2 = `NO3+NO2`)
# cleanup and convert in umol/kg
d_all <- left_join(d_all, nuts, by = c("datetime" = "closest")) #%>% 
  #dplyr::select(-closest_datetime)
d_all <- d_all %>% 
  dplyr::mutate(density_fb = seacarb::rho(S = sal_fb, T = temp_fb, P = 0),
                PO4 = PO4 / (density_fb/1000),
                NH4 = NH4 / (density_fb/1000),
                NO3NO2 = NO3NO2 / (density_fb/1000),
                NO3 = NO3 / (density_fb/1000),
                Si = Si / (density_fb/1000)
  )
```

@@

## Impact of nutrients
```{r impact of nutrients, echo=FALSE, warning=TRUE, message=FALSE}
# boxplot
ts_PO4_bp <- d_all %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = PO4)) +
  #geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm = TRUE) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
  labs(y = "PO4", x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())

ts_Si_bp <- d_all %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = Si)) +
  #geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm = TRUE) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
  labs(y = "Si", x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
ts_Si_bp + ts_Si_bp
# Effects of changes in PO4 and Si
# 1st cakculate mean values
means <- d_all %>% 
  group_by(montht) %>% 
  summarize(mean_ct = mean(ct, na.rm = TRUE),
            mean_at_calc = mean(at_calc, na.rm = TRUE),
            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
            mean_sal = mean(sal_fb, na.rm = TRUE),
            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
  ungroup()
mean_ct <-  mean(means$mean_ct)
mean_at_calc <-  mean(means$mean_at_calc)
mean_pco2_calc <-  mean(means$mean_pco2_calc)
mean_sal <-  mean(means$mean_sal)
mean_temp <-  mean(means$mean_temp)
# then check impacts using pco2 and AT
carb_PO4_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = c(min(d_all$PO4/1e6, na.rm=TRUE), max(d_all$PO4/1e6, na.rm=TRUE)), Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_PO4_1 <- carb_PO4_1[1,] - carb_PO4_1[2,]
carb_Si_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = c(min(d_all$Si/1e6, na.rm=TRUE), max(d_all$Si/1e6, na.rm=TRUE)), 
                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_Si_1 <- carb_Si_1[1,] - carb_Si_1[2,]

# then check impacts using AT-DIC pair
carb_PO4_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = c(min(d_all$PO4/1e6, na.rm=TRUE), max(d_all$PO4/1e6, na.rm=TRUE)), Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_PO4_2 <- carb_PO4_2[1,] - carb_PO4_2[2,]
carb_Si_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = c(min(d_all$Si/1e6, na.rm=TRUE), max(d_all$Si/1e6, na.rm=TRUE)), 
                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_Si_2 <- carb_Si_2[1,] - carb_Si_2[2,]
```

The concentration of PO4 and Si varies with a factor 10 along a composite year. The ranges are respectively, `r round(range(d_all$PO4, na.rm = TRUE), digits = 2)` for PO4 and `r round(range(d_all$Si, na.rm = TRUE), digits = 2)` for Si.

### Using the pCO2-AT pair (hourly data)
The impact of the min max changes of PO4 on pH, DIC, and Omega_a are small:  `r round(1000*diff_PO4_1$pH, digits=2)` mpH units, `r round(1e6*diff_PO4_1$DIC, digits=2)` umol/kg for CT and `r round(diff_PO4_1$OmegaAragonite, digits=2)` for OmegaAragonite.

The impact of the min max changes of Si on pH, DIC, and Omega_a are small:  `r round(1000*diff_Si_1$pH, digits=2)` mpH units, `r round(1e6*diff_Si_1$DIC, digits=2)` umol/kg for CT and `r round(diff_Si_1$OmegaAragonite, digits=2)` for OmegaAragonite.

### Using the CT-AT pair (discrete data)
The impact of the min max changes of PO4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_PO4_2$pH, digits=2)` mpH units, `r round(diff_PO4_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_PO4_2$OmegaAragonite, digits=2)` for OmegaAragonite.

The impact of the min max changes of PO4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_Si_2$pH, digits=2)` mpH units, `r round(diff_Si_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_Si_2$OmegaAragonite, digits=2)` for OmegaAragonite.

@@

Si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.
Pattern des commandes : # m h dom mon dow command

>>>>

---
title: "Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project" 
author: "Jean-Pierre Gattuso and Samir Alliouane"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::
  rmarkdown::html_document:
    theme: paper
    number_sections: false

@@

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
if (!require("tidyverse")) install.packages("tidyverse")
library(dplyr)
library(tidyverse)
if (!require("robfilter")) install.packages("robfilter")
if (!require("robfilter")) install.packages("robfilter")
library("robfilter")
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("reshape2")) install.packages("reshape2")
library("reshape2")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("lmtest")) install.packages("lmtest")
library("lmtest")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("seismicRoll")) install.packages("seismicRoll")
library("seismicRoll")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("cowplot")) install.packages("cowplot")
library(cowplot)
if (!require("htmlwidgets")) install.packages("htmlwidgets")
library("htmlwidgets")
if (!require("hms")) install.packages("hms")
library("hms")
if (!require("ragg")) install.packages("ragg")
library("ragg")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")

@@

```{r read data, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2 = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  arrange(datetime)
d_all <- as_tibble(d_hour) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & pressure_insitu_ctd <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & pressure_insitu_ctd <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & pressure_insitu_ctd <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 9, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
  )
```

@@

# create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_fb <- NA
discrete_is_na$pco2_calc_fb <- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)
```
```{r read and prepare nutrient data, echo=FALSE, warning=TRUE, message=FALSE}
# File "Ferrybox nutrients 2014-2018.xlsx" provided by 
# Willem van de Poll <w.h.van.de.poll@rug.nl> on 2020-01-16
# nutrients in umol/l
nuts <- readxl::read_excel(paste0(path, "fb_data/Ferrybox nutrients 2014-2018.xlsx"),
                           skip =1) %>% 
  drop_na(date) %>% 
  dplyr::mutate(datetime = as.POSIXct(paste0(date, " 12:00:00"))) %>% # assuming sampling time 12:00
  dplyr::filter(datetime > as.POSIXct("2015-07-09"))
# The nearest times
time_index <- unique(d_all$datetime)
# nuts$closest <- time_index[
#   FNN::knnx.index(time_index, # The values to be queried (big df)
#                   as.vector(nuts$datetime), # The value to find the closest match to (small df)
#                   k = 1)] # The number of closest values to return
nuts <- nuts %>% 
  dplyr::mutate(closest = time_index[
  FNN::knnx.index(time_index, # The values to be queried (big df)
                  as.vector(nuts$datetime), # The value to find the closest match to (small df)
                  k = 1)]) %>%  # The number of closest values to return
  dplyr::select(-date, -datetime) %>% 
  dplyr::rename(no3no2 = `no3+no2`)
# cleanup and convert in umol/kg
d_all <- left_join(d_all, nuts, by = c("datetime" = "closest")) #%>% 
  #dplyr::select(-closest_datetime)
d_all <- d_all %>% 
  dplyr::mutate(density_fb = seacarb::rho(S = sal_fb, T = temp_fb, P = 0),
                po4 = po4 / (density_fb/1000),
                nh4 = nh4 / (density_fb/1000),
                no3no2 = no3no2 / (density_fb/1000),
                no3 = no3 / (density_fb/1000),
                si = si / (density_fb/1000)
  )
```

@@

## Impact of nutrients
```{r impact of nutrients, echo=FALSE, warning=FALSE, message=FALSE}
# boxplot
ts_po4_bp <- d_all %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = po4)) +
  #geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm = TRUE) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
  labs(y = "po4", x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())

ts_Si_bp <- d_all %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = si)) +
  #geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm = TRUE) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
  labs(y = "si", x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
ts_Si_bp + ts_Si_bp
# Effects of changes in po4 and si
# 1st cakculate mean values
means <- d_all %>% 
  group_by(montht) %>% 
  summarize(mean_ct = mean(ct, na.rm = TRUE),
            mean_at_calc = mean(at_calc, na.rm = TRUE),
            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
            mean_sal = mean(sal_fb, na.rm = TRUE),
            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
  ungroup()
mean_ct <-  mean(means$mean_ct)
mean_at_calc <-  mean(means$mean_at_calc)
mean_pco2_calc <-  mean(means$mean_pco2_calc)
mean_sal <-  mean(means$mean_sal)
mean_temp <-  mean(means$mean_temp)
# then check impacts using pco2 and AT
carb_po4_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = c(min(d_all$po4/1e6, na.rm=TRUE), max(d_all$po4/1e6, na.rm=TRUE)), Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_po4_1 <- carb_po4_1[1,] - carb_po4_1[2,]
carb_Si_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = c(min(d_all$si/1e6, na.rm=TRUE), max(d_all$si/1e6, na.rm=TRUE)), 
                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_Si_1 <- carb_Si_1[1,] - carb_Si_1[2,]

# then check impacts using AT-DIC pair
carb_po4_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = c(min(d_all$po4/1e6, na.rm=TRUE), max(d_all$po4/1e6, na.rm=TRUE)), Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_po4_2 <- carb_po4_2[1,] - carb_po4_2[2,]
carb_Si_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = c(min(d_all$si/1e6, na.rm=TRUE), max(d_all$si/1e6, na.rm=TRUE)), 
                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_Si_2 <- carb_Si_2[1,] - carb_Si_2[2,]
```

The concentration of po4 and si varies with a factor 10 along a composite year. The ranges are respectively, `r round(range(d_all$po4, na.rm = TRUE), digits = 2)` for po4 and `r round(range(d_all$si, na.rm = TRUE), digits = 2)` for si.

### Using the pCO2-AT pair (hourly data)
The impact of the min max changes of po4 on pH, DIC, and Omega_a are small:  `r round(1000*diff_po4_1$pH, digits=2)` mpH units, `r round(1e6*diff_po4_1$DIC, digits=2)` umol/kg for CT and `r round(diff_po4_1$OmegaAragonite, digits=2)` for OmegaAragonite.

The impact of the min max changes of si on pH, DIC, and Omega_a are small:  `r round(1000*diff_Si_1$pH, digits=2)` mpH units, `r round(1e6*diff_Si_1$DIC, digits=2)` umol/kg for CT and `r round(diff_Si_1$OmegaAragonite, digits=2)` for OmegaAragonite.

### Using the CT-AT pair (discrete data)
The impact of the min max changes of po4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_po4_2$pH, digits=2)` mpH units, `r round(diff_po4_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_po4_2$OmegaAragonite, digits=2)` for OmegaAragonite.

The impact of the min max changes of po4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_Si_2$pH, digits=2)` mpH units, `r round(diff_Si_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_Si_2$OmegaAragonite, digits=2)` for OmegaAragonite.

## Impact of choice of constants
### Using mean values
```{r impact of constants, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
# use mean values calculated for impacts of nutrients above
means <- d_all %>% 
  group_by(montht) %>% 
  summarize(mean_ct = mean(ct, na.rm = TRUE),
            mean_at_calc = mean(at_calc, na.rm = TRUE),
            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
            mean_sal = mean(sal_fb, na.rm = TRUE),
            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
  ungroup()
mean_ct <-  mean(means$mean_ct)
mean_at_calc <-  mean(means$mean_at_calc)
mean_pco2_calc <-  mean(means$mean_pco2_calc)
mean_sal <-  mean(means$mean_sal)
mean_temp <-  mean(means$mean_temp)
# impacts using pco2 and AT
carb_l_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_1 <- carb_l_1 - carb_s_1

# impacts using AT-DIC pair
carb_l_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = 0, 
                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_2 <- carb_l_2 - carb_s_2
const <- bind_rows(diff_ls_1, diff_ls_2) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
                S = mean_sal,
                T = mean_temp,
                DIC = DIC * 1e6
                ) %>% 
  dplyr::select(flag:T, pH, pCO2, DIC, OmegaAragonite)
#kable(const, digits = c(0, 1, 1, 3, 1, 1, 2))
pander(const)
```
### Using all values pCO2 and at_calc
```{r impact of constants, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
d_ls <- d_all %>% 
  drop_na(pco2_corr, at_calc, sal_fb, temp_fb)
carb_l <-
  carb(
    24,
    d_ls$pco2_corr,
    d_ls$at_calc * 1e-6,
    S = d_ls$sal_fb,
    T = d_ls$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "l",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
carb_s <-
  carb(
    24,
    d_ls$pco2_corr,
    d_ls$at_calc * 1e-6,
    S = d_ls$sal_fb,
    T = d_ls$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "s20",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
diff_ls <- as_tibble(carb_l - carb_s)
d_ls <- bind_cols(d_ls, diff_ls)

# plot
lm <- lm2(x = tmp$sal_insitu_ctd_9m, y = d_all$sal_fb)
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(monthd))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()

print(p) #p_sal_fb_ctd
```

The difference induces by the choice of the carbonic acid constants is large for pH, pCO2 and DIC and negligible for OmegaAragonite.

@@

si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.
Pattern des commandes : # m h dom mon dow command
